RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-03-02 paper/paper7/paper7.tex
implementation

With \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{www.gesis.org/en/missy/linked-data}}} like a \textcolor{red}{triple store} and exports of person-level metadata to Disco RDF in multiple concrete syntaxes (e.g. turtle).

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
We use the \emph{SPIN}\footnote{\url{http://spinrdf.org/}}, 
a SPARQL-based way to formulate and check constraints, as basis to define a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) \cite{BoschEckert2014-2}.
The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
Within the validation environment, we define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint \footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.

- Validation of Data Cube instances

>>>>

In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{www.gesis.org/en/missy/linked-data}}} like a \textcolor{red}{triple store} and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g. turtle).

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
We use \emph{SPIN}\footnote{\url{http://spinrdf.org/}}, 
a SPARQL-based way to formulate and check constraints, as basis to define a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions\footnote{\url{http://www.w3.org/Submission/shex-primer/}} and the Web Ontology Language \cite{BoschEckert2014-2}.
The \emph{RDF Validator} also validates RDF data conforming to SPARQL constraints to ensure correct syntax and semantics of vocabularies such as \emph{Disco, Data Cube, PHDD, DCAT, SKOS, and XKOS}.
The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
We define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject, the properties causing constraint violations, and the reason why constraint violations have been raised.
A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
